Semantic Preserving Bijective Mappings for Representations of Special Functions between Computer Algebra Systems and Word Processors

### 2018-07-31 main.tex
Howards updates

\section{Conclusion \& Future Work}\label{ch:conc-future-work}
The results and conclusions of the translations of the formula set from the \DLMF{} are diverse. Some test cases have shown us that the set of semantic macros are not perfect yet and need to be improved. This is seen in the example of the macro definition for the Wronskian determinant. However, simply adding more and more macros to improve the set is not the right decision. In that case, we would end up in something similar to \sTeX, which is overloaded and too complicated to use. If the system is no longer handy, it will not be used {\bf [HSC: I don't agree with this paragraph. In fact, I think we've had this discussion already in the past and it was resolved. It needs to be resolved again. There are many examples where enhancing macros is a benefit. Not only that, we've discussed this recently in our publications. This needs to be fixed prior to submission.]}

>>>>

\section{Conclusion \& Future Work}\label{ch:conc-future-work}
The results and conclusions of the translations of the formula set from the \DLMF{} are diverse. Some test cases have shown us that the set of semantic macros are not perfect yet and need to be improved. This is seen in the example of the macro definition for the Wronskian determinant. However, simply adding more and more macros to improve the set is not the right decision. In that case, we would end up in something similar to \sTeX, which is overloaded and too complicated to use. If the system is no longer handy, it will not be used {\bf [HSC: I don't agree with this paragraph at all. In fact, I think we've had this discussion already in the past and it was resolved. It needs to be resolved again. There are many examples where enhancing macros is a benefit. Not only that, we've discussed this recently in our publications. This needs to be fixed prior to submission. I vote for removing this paragraph altogether until we can resolve this issue.]}
